---
title: "Sample Size - Grand Bassa Stepped Wedge"
# output: html_document
# output: pdf_document
output: word_document
editor_options:
  chunk_output_type: console
---



# Configuration
- Manually modify this section to control simulation configuration
- `levels` specifies a list of "simulation levels", the simulation will be done for each combination of levels
- `num_sim` controls the number of simulations to be done for each level combination
- `constants` is a list of variables that remain constant across all simulations. It includes `parallel`, which can take on one of the following values:
    - "inner": parallelization is done within a single simulation
    - "outer": parallelization is done across multiple simulations, i.e. one simulation per thread/node
    - "none": no parallelization is done; useful for debugging
```{r}

# Define simulation levels
# `levels` should not be accessed globally. Instead, within run_one_simulation(), call levels_row$dimension_1, etc.
levels <- list(
  "dimension_1" = c(33,44,55),
  "dimension_2" = c(10,100,1000)
)

# Define number of simulations per level
num_sim <- 3

# Define simulation constants
# `constants` should be accessed globally
# `parallel` can be set to "inner", "outer", or "none"
constants <- list(
  "parallel" = "inner",
  "n" = 10,
  "constant_2" = 123
)

# Define list of functions/globals to export to cluster
# Try to avoid passing in globals if possible
cluster_export = c("run_one_simulation", "levels_grid", "constants",
                   "create_dataset", "levels_row")

# When running on cluster, catch config variables via `argparse`
# When running locally, set config variables in the `else` section
if (exists("p_args")) {
  var_1 <- p_args$var_1
  var_2 <- p_args$var_2
} else {
  
  # Description of `var_1`
  var_1 <- NA
  
  # Description of `var_2`
  var_2 <- NA
  
}

```



# Load libraries
```{r warning=FALSE, message=FALSE}

# Set `libloc` variable if script is running locally
# Note: `libloc` variable set in `run_rmd.R`
if (!exists("libloc")) { libloc <- .libPaths() }

# Load libraries
# Note: `libloc` variable set in `run_rmd.R`
library(parallel, lib.loc=libloc)
library(ggplot2, lib.loc=libloc)
# ...

```



# Setup
- This section will not typically need to be modified
```{r}

# Remove variables set in `run_rmd.R`
if (exists("path")) { rm(path) }
if (typeof(file)!="closure") { rm(file) }

# Set up cluster
n_cores <- detectCores() - 1
cl <- makeCluster(n_cores)

# Set placeholder variables
levels_row <- ""

# # Set up time log
# # Note: does not work in parallel; for debugging only
# times <- c("Start time", round(as.numeric(Sys.time()),1))
# log_time <- function(label) {
#   times <<- c(
#     times,
#     label,
#     round(as.numeric(Sys.time()) - as.numeric(times[2]), 1)
#   )
# }
# display_log <- function() {
#   for (i in 1:length(times)) {
#     print(times[i])
#   }
# }

```



# Run code
```{r}

# Declare functions
# Note: if running this locally in RStudio, you may need to click "Session" >> "Set Working Directory" >> "To Source File Location"
source('create_dataset.R')
source('run_one_simulation.R')
source('analyze_results.R')

# Create data frame of simulation levels
levels[["sim_sub_index"]] <- seq(from=1, to=num_sim)
levels_grid <- expand.grid(levels)
levels_names <- names(levels_grid)
levels_grid <- cbind(1:nrow(levels_grid), levels_grid)
names(levels_grid) <- c("sim_index",levels_names)

# Run simulations
if (constants$parallel == "outer") {
  
  # Export variables/functions
  clusterExport(cl, cluster_export)
  
  # Run in parallel
  results_lists <- parLapply(cl, 1:nrow(levels_grid), function(i) {
    run_one_simulation(i, as.list(levels_grid[i,]), constants)
  })
  
} else {
  
  # Run in series
  results_lists <- lapply(1:nrow(levels_grid), function(i) {
    run_one_simulation(i, as.list(levels_grid[i,]), constants)
  })
  
}

# Convert summary statistics to data frame
summary_lists <- list()
for (i in 1:length(results_lists)) {
  summary_lists[[i]] <- c(
    list("sim_index" = results_lists[[i]]$sim_index[[1]]),
    results_lists[[i]]$summary
  )
}
summary <- data.frame(
  matrix(
    unlist(summary_lists),
    nrow = length(summary_lists),
    byrow = TRUE
  )
)
names(summary) <- names(summary_lists[[1]])

# Join `results` with `levels_grid`
summary <- dplyr::inner_join(levels_grid, summary, by="sim_index")

# Analyze / view results
analyze_results(results_list, summary)

```
