---
title: "Sample Size - Grand Bassa Stepped Wedge"
# output: html_document
# output: pdf_document
output: word_document
editor_options:
  chunk_output_type: console
---



# Load libraries
```{r warning=FALSE, message=FALSE}

# Set `libloc` variable if script is running locally
# Note: `libloc` variable set in `run_rmd.R`
if (!exists("libloc")) { libloc <- .libPaths() }

# Load libraries
# Note: `libloc` variable set in `run_rmd.R`
library(parallel, lib.loc=libloc)
library(ggplot2, lib.loc=libloc)
library(readxl, lib.loc=libloc)
library(magrittr, lib.loc=libloc)
library(dplyr, lib.loc=libloc)
library(tibble, lib.loc=libloc)
library(rlist, lib.loc=libloc)
# ...

```



# Configuration
- Manually modify this section to control simulation configuration
- `levels` specifies a list of "simulation levels", the simulation will be done for each combination of levels
simulation
    - "one": use the same dataset for all simulations
    - "many": generate a new dataset for each simulation
- `config` is a list of variables that remain constant across all simulations. It includes the following:
    - `num_sim` controls the number of simulations to be done for each level combination
    - `datasets` specifies whether to use one generated dataset for all simulations versus generating a new dataset for each simulation
    - `parallel` controls which sections of the code are parallelized (i.e. for speed gains on multicore/cluster computing systems). It can take on one of the following values:
        - "inner": parallelization is done within a single simulation
        - "outer": parallelization is done across multiple simulations, i.e. one simulation per thread/node
        - "none": no parallelization is done; useful for debugging
- `constants` is a list of simulation-specific variables that remain constant across all simulations.
```{r}

# Define simulation levels
# `levels` should not be accessed globally. Instead, within run_one_simulation(), call levels_row$dimension_1, etc.
levels <- list(
  "n_clusters" = c(100,200,400)
)

# Define simulation configuration constants
# `config` should be accessed globally
config <- list(
  "num_sim" = 3,
  "datasets" = "many",
  "parallel" = "inner"
)

# Define simulation constants
# `constants` should be accessed globally
constants <- list(
  "sampling_frame" = read_excel(
    "data/GrandBassa2020SamplingFrame_truncated.xlsx"
  ) %>%
    rowid_to_column("community_id") %>%
    rename(
      'num_hh' = `numHH`,
      'health_district' = `map_health_district`,
      'admin_district' = `map_adm_distri`
    )
)

# Define list of functions/globals to export to cluster
# Try to avoid passing in globals if possible
cluster_export = c(
  "run_one_simulation", "levels_grid", "config", "constants",
  "create_dataset", "levels_row", "dataset", "list.filter"
)

```



# Setup
- This section will not typically need to be modified
```{r}

# Remove variables set in `run_rmd.R`
if (exists("path")) { rm(path) }
if (exists("num")) { rm(num) }
if (typeof(file)!="closure") { rm(file) }

# Set up cluster
n_cores <- detectCores() - 1
cl <- makeCluster(n_cores)

# Set placeholder variables
levels_row <- ""

```



# Run code
```{r}

# Declare functions
# Note: if running this locally in RStudio, you may need to click "Session" >> "Set Working Directory" >> "To Source File Location"
source('R/create_dataset.R')
source('R/take_sample.R')
source('R/birth_history.R')
source('R/run_one_simulation.R')
source('R/analyze_results.R')

# Create data frame of simulation levels
levels[["sim_sub_index"]] <- seq(from=1, to=config$num_sim)
levels_grid <- expand.grid(levels)
levels_names <- names(levels_grid)
levels_grid <- cbind(1:nrow(levels_grid), levels_grid)
names(levels_grid) <- c("sim_index",levels_names)

# Run simulations
if (config$parallel == "outer") {
  
  # Generate dataset
  # Note: when config$dataset == "one", create_dataset() should not depend on levels_grid
  if (config$dataset == "one") {
    dataset <- create_dataset(
      sampling_frame = constants$sampling_frame,
      parallel_inner = ifelse(
        config$parallel=="inner", TRUE, FALSE
      ),
      levels_row = as.list(levels_grid[1,]),
      program_effect = TRUE # !!!!! Placeholder
    )
  } else {
    dataset <- NULL
  }
  
  # Export variables/functions
  clusterExport(cl, cluster_export)
  
  # Run in parallel
  results_lists <- parLapply(
    cl,
    1:nrow(levels_grid),
    function(i) {
      run_one_simulation(
        i,
        as.list(levels_grid[i,]),
        constants,
        dataset
      )
    }
  )
  
} else {
  
  # Run in series
  results_lists <- lapply(1:nrow(levels_grid), function(i) {
    run_one_simulation(i, as.list(levels_grid[i,]), constants)
  })
  
}

# Convert summary statistics to data frame
summary_lists <- list()
for (i in 1:length(results_lists)) {
  summary_lists[[i]] <- c(
    list("sim_index" = results_lists[[i]]$sim_index[[1]]),
    results_lists[[i]]$summary
  )
}
summary <- data.frame(
  matrix(
    unlist(summary_lists),
    nrow = length(summary_lists),
    byrow = TRUE
  )
)
names(summary) <- names(summary_lists[[1]])

# Join `results` with `levels_grid`
summary <- dplyr::inner_join(levels_grid, summary, by="sim_index")

# Analyze / view results
analyze_results(results_list, summary)

```
